### 2014-10-22 Studies/2013_PG_County/Report/PG_Co_Fire.tex
PG_Co: minor update to report

\vspace{0.2in}

\begingroup
{\bf This publication is available free of charge from:}
\hypersetup{urlcolor=black}
\href{http://dx.doi.org/10.6028/NIST.TN.XXXX}{\bf http://dx.doi.org/10.6028/NIST.TN.XXXX} \\
\endgroup

@@

\begin{figure}[!ht]
\includegraphics[width=.5\textwidth]{../Figures/PGCo_Slope}
\includegraphics[width=.5\textwidth]{../Figures/pg_county_slope} \\
\caption[Photograph of terrain.]{Photograph taken from front side street level showing the slope down to basement on the rear side of the structure (left) and Smokeview rendering of model representation of sloped landscape (right).}
\label{fig:slope}
\end{figure}

>>>>

@@

\begin{figure}[!ht]
\includegraphics[width=.5\textwidth]{../Figures/PGCo_Slope}
\includegraphics[width=.5\textwidth]{../Figures/pg_county_slope} \\
\caption[Photograph and computer model rendering of terrain.]{Photograph taken from front side street level showing the slope down to basement on the rear side of the structure (left) and Smokeview rendering of model representation of sloped landscape (right).}
\label{fig:slope}
\end{figure}
